Highlights of NIPS 2016

### 2017-01-12 Highlights/slides.tex
[major] second update to slides for highlights presentation

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{bnn2.png}
    \end{figure}

@@

    \begin{itemize}
      \item \href{http://people.eecs.berkeley.edu/~pabbeel/nips-tutorial-policy-optimization-Schulman-Abbeel.pdf}{Deep RL through Policy Optimization\footnotemark[1]}:
        \begin{itemize}
          \item History of policy search RL
          \item Recent trends with DNN policies presented
          \item Future work on \textbf{Skill Transfer} and \textbf{Exploration}
        \end{itemize}
      \item \href{http://rll.berkeley.edu/deeprlcourse/docs/nuts-and-bolts.pdf}{Nuts and Bolts of Deep RL Research\footnotemark[2]}:
        \begin{itemize}
          \item Tips on implementing existing algorithms
          \item Problem formulation for novel tasks
        \end{itemize}
    \end{itemize}

    \begin{columns}
      \begin{column}
        \begin{figure}
          \centering
          \includegraphics[width=0.8\textwidth]{}
        \end{figure}
      \end{column}
      \begin{column}
        \begin{figure}

        \end{figure}
      \end{column}
    \end{columns}
    \footnotetext[1]{Tutorial by Pieter Abbeel and John Schulman}
    \footnotetext[2]{Tutorial by John Schulman in Deep RL Workshop}
  \end{frame}

  \begin{frame}
    \frametitle{Deep Reinforcement Learning: Workshop}

  \begin{frame}
    \frametitle{Value Iteration Networks}

@@

>>>>

    \begin{figure}
      \centering
      \includegraphics[width=0.75\textwidth]{bnn2.png}
    \end{figure}

@@

    \begin{itemize}
      \item \href{http://people.eecs.berkeley.edu/~pabbeel/nips-tutorial-policy-optimization-Schulman-Abbeel.pdf}{Deep RL through Policy Optimization\footnotemark[1]}:
        \begin{itemize}
          \item History of policy search RL focusing on Deep RL
          \item Future work on \textbf{Skill Transfer} and \textbf{Exploration}
        \end{itemize}
      \item \href{http://rll.berkeley.edu/deeprlcourse/docs/nuts-and-bolts.pdf}{Nuts and Bolts of Deep RL Research\footnotemark[2]}:
        \begin{itemize}
          \item Tips on implementing existing algorithms
          \item Problem formulation for novel tasks
        \end{itemize}
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{drl1.png}
    \end{figure}

    \footnotetext[1]{Tutorial by Pieter Abbeel and John Schulman}
    \footnotetext[2]{Tutorial by John Schulman in Deep RL Workshop}
  \end{frame}

  \begin{frame}
    \frametitle{Opensource Environments}

    \begin{itemize}
      \item OpenAI Universe\footnotemark[1]: Develop and implement RL algorithms on many environments.
      \item Google Deepmind\footnotemark[2]: Simulator of 3D environments such as \textbf{Quake} and puzzle tasks.
      \item Facebook TorchCraft\footnotemark[3]: Bridge between Torch Library and Starcraft Game.
    \end{itemize}
    \vskip-1.5em
    \begin{columns}
      \begin{column}{0.33\textwidth}
        \begin{figure}
          \centering
          \caption*{OpenAI Universe}
          \includegraphics[width=0.8\textwidth]{drlApp1.png}
        \end{figure}
      \end{column}
      \begin{column}{0.33\textwidth}
        \begin{figure}
          \centering
          \caption*{Google Deepmind}
          \includegraphics[width=0.8\textwidth, height=0.25\textheight]{drlApp2.png}
        \end{figure}
      \end{column}
      \begin{column}{0.33\textwidth}
        \begin{figure}
          \centering
          \caption*{Facebook Starcraft}
          \includegraphics[width=0.8\textwidth]{drlApp3.png}
        \end{figure}
      \end{column}
    \end{columns}

    \footnotetext[1]{\href{https://openai.com/blog/universe/}{OpenAI Universe Press Release}}
    \footnotetext[2]{\href{https://deepmind.com/blog/open-sourcing-deepmind-lab/}{Google Deepmind Blog}}
    \footnotetext[3]{\href{https://github.com/TorchCraft/TorchCraft}{TorchCraft Repository on Github}}
  \end{frame}

  \begin{frame}
    \frametitle{Value Iteration Networks: Best Paper Award}

    \centering
    Represent Bellman equations with Convolutional Neural Networks to learn Value function
    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{drl2.png}
    \end{figure}

    \footnotetext[1]{Tamar et al., ``Value Iteration Networks'' in \emph{NIPS 2016}}
  \end{frame}

@@

    \begin{itemize}
      \item Papers on theoretical foundations (\textbf{better architectures}\footnotemark[1]) and applications (\textbf{Reinforcement Learning}\footnotemark[2]).
      \item Strong correspondence to Neuroscience research (Fast and Slow time scales\footnotemark[3]).
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{rnn1.png}
    \end{figure}

    \footnotetext[1]{}
  \end{frame}
